Paper_analyses

### 2021-08-25 IAPS_PREPROCESSING_2021_1.Rmd
fixing missing behavioural data in 245_355

tmp.df4_sum_full_bio_hr_self_parsed
write_csv(tmp.df4_sum_full_bio_hr_self_parsed, 'tmp.df4_sum_full_bio_hr_self_parsed_345_356.csv')
write_csv(tmp.df4, 'tmp.df4_timeseries_345_356.csv')

@@

tmp.df4_sum_full_bio_hr_self_parsed$TAS
tmp.df4_sum_full_bio_hr_self_parsed %>%
  subset(screencontent_no>2)%>%
  group_by(ssid)%>%
  summarise_if(is.numeric,mean, na.rm = TRUE)%>%
  ggplot(aes(Age,sdev_gazesum))+
  geom_point()+
  geom_smooth(method = lm, se = F)

>>>>

tmp.df4_sum_full_bio_hr_self_parsed

# merge behavioural data
db_beh3$ssid<- as.character(db_beh3$ssid)
db_beh3$tNo <- as.character(db_beh3$tNo)
tmp.df4_sum_full_bio_hr_self_parsed$tNo<- as.character(tmp.df4_sum_full_bio_hr_self_parsed$tNo)
# tmp.df4_sum_full<-

tmp.df4_sum_full_bio_hr_self_parsed<- left_join(tmp.df4_sum_full_bio_hr_self_parsed, db_beh3, by = c('ssid', 'tNo'))

View(db_beh3)
tmp.df4_sum_full<- tmp.df4_sum_full%>%
  arrange(ssid, tNo, time)

@@

tmp.df4_sum_full_bio_hr_self_parsed$TAS
# tmp.df4_sum_full_bio_hr_self_parsed<- tmp.df4_sum_full_bio_hr_self_parsed %>%
#   subset(screencontent_no>2)%>%
#   group_by(ssid)%>%
#   summarise_if(is.numeric,mean, na.rm = TRUE)%>%
#   ggplot(aes(Age,sdev_gazesum))+
#   geom_point()+
#   geom_smooth(method = lm, se = F)

colnames(tmp.df4_sum_full_bio_hr_self_parsed)

tmp.df4_sum_full_bio_hr_self_parsed$Age<- tmp.df4_sum_full_bio_hr_self_parsed$age_response_specific
tmp.df4_sum_full_bio_hr_self_parsed$gender<- substr(tmp.df4_sum_full_bio_hr_self_parsed$gender_response,1,1)

tmp.df4_sum_full_bio_hr_self_parsed$BIO_filename<- NULL
tmp.df4_sum_full_bio_hr_self_parsed$`Participant Completion Code`<- NULL
tmp.df4_sum_full_bio_hr_self_parsed$`Participant Private ID`<- NULL

tmp.df4_sum_full_bio_hr_self_parsed$`Participant No`<- NULL
tmp.df4_sum_full_bio_hr_self_parsed$age_response_specific<- NULL
tmp.df4_sum_full_bio_hr_self_parsed$Event.NID<- NULL
tmp.df4_sum_full_bio_hr_self_parsed$`Event Index`<- NULL
tmp.df4_sum_full_bio_hr_self_parsed$gender_response<- NULL

tmp.df4_sum_full_bio_hr_self_parsed$`Person testing`<- NULL
tmp.df4_sum_full_bio_hr_self_parsed$Event.Nr.x<- NULL
tmp.df4_sum_full_bio_hr_self_parsed$filename.x<- NULL
tmp.df4_sum_full_bio_hr_self_parsed$filename.y<- NULL

tmp.df4_sum_full_bio_hr_self_parsed

tmp.df4_sum_full_bio_hr_self_parsed<- tmp.df4_sum_full_bio_hr_self_parsed%>%
  rename(IAS = IAS_score)%>%
  rename(ASD_self = ASD)

tmp.df4_sum_full_bio_hr_self_parsed1<- select(tmp.df4_sum_full_bio_hr_self_parsed,)

write_csv(tmp.df4_sum_full_bio_hr_self_parsed, 'tmp.df4_sum_full_bio_hr_self_parsed_345_356.csv')
write_csv(tmp.df4, 'tmp.df4_timeseries_345_356.csv')
```

### 2021-08-25 Paper_Analyses_subj_obje_arousal.Rmd
fixing missing behavioural data in 245_355

colnames(db_full4new_stim_screen_pupil_nopract)

participants_demog <- db_full4new_stim_screen_pupil_nopract %>%
  subset(Group == "NT")%>%
  group_by(ssid, Gender)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)

>>>>

colnames(db_345_355)

# db_345_355_1<- select(db_345_355, c(1:41, )
colnames(db_full4new_stim_screen_pupil_nopract)

db_345_355_stim<- subset(db_345_355, db_345_355$screencontent == "stim")

db_full4new_stim_screen_pupil_nopract$ssid<- as.character(db_full4new_stim_screen_pupil_nopract$ssid)
db_345_355_stim$ssid<- as.character(db_345_355_stim$ssid)
db_345_355_stim$tNo<- as.character(db_345_355_stim$tNo)

colnames(db_full4new_stim_screen_pupil_nopract)
colnames(db_345_355_stim)

install.packages("gtools")
?gtools::smartbind()

# binf only common columns

outersect <- function(x, y) {
  sort(c(setdiff(x, y),
         setdiff(y, x)))
}

common_cols

oposite_columns<- outersect(colnames(db_full4new_stim_screen_pupil_nopract), colnames(db_345_355_stim$age_response_specific))

common_cols
oposite_columns
rbind(
  db_full4new_stim_screen_pupil_nopract[common_cols], 
  db_345_355_stim[common_cols]
)

colnames(db_full4new_stim_screen_pupil_nopract)
colnames(db_345_355_stim)

db_full4new_stim_screen_pupil_nopract
db_345_355_stim$gender_response

db_345_355_stim<- db_345_355_stim %>% 
  rename(Age = age_response_specific)%>%
  rename(Gender = gender_response)
db_345_355_stim$Age<- age_response_specific

db_full4new_stim_screen_pupil_nopract<- bind_rows(db_full4new_stim_screen_pupil_nopract, db_345_355_stim)
```

```{r}
unique(db_full4new_stim_screen_pupil_nopract$Group)
db_full4new_stim_screen_pupil_nopract$Group<- if_else(as.numeric(db_full4new_stim_screen_pupil_nopract$ssid) < 500, "NT",                                               if_else(as.numeric(db_full4new_stim_screen_pupil_nopract$ssid) > 700,"NT", "ASD"))

db_full4new_stim_screen_pupil_nopract$Group_t<- NULL

unique(db_full4new_stim_screen_pupil_nopract$Group_t)

# db_full4new_stim_screen_pupil_nopract$grou

db_full4new_stim_screen_pupil_nopract$Gender<- substr(db_full4new_stim_screen_pupil_nopract$Gender, 1,1)
participants_demog <- db_full4new_stim_screen_pupil_nopract %>%
  subset(Group == "NT")%>%
  group_by(ssid, Gender)%>%
  summarise_at(c("Age","WASIM", "TAS", "AQ", "IAS", "DASSTotal"), mean, na.rm = TRUE)
